---
title: "Assignment 2"
author: "Group 4"
date: "Nov 9 2015"
output: html_document
---

<!-- KOMMENTAR
Kan vi lave "rigtige" referencer?
Hvor mange mandage er der i perioden?
In the section on ration cards: What about outliers?
-->

*Chris, Sune, Jeppe and Nina*

```{r, echo=FALSE, message=FALSE}
# Read libraries
library(rvest)
library(stringr)
library(lubridate)
library(ggplot2)
library(dplyr)
library(readr)
library(scales)

# Load dataset
df = read_csv("https://raw.githubusercontent.com/Ninaholst/SDS-group-4/master/bribes.csv")
df$week_day = wday(df$date, label = TRUE, abbr = FALSE)
df = filter(df, amount < 10000000) # remove insane outliers
```

# Introduction to data

The dataset analyzed in this assignment contains 1000 observations on self-reported bribes in India from 12th to 30th of October 2015. The data was scraped from the webpage http://www.ipaidabribe.com/. It contains information about when and where in the system the bribe took place, the geographical location and what kind of transaction the bribe was related to.

Monday the 12th of October 2015 is overrepresented in the dataset, 734 of the 1000 bribes were reported this Monday. When you look at different variables grouped by weekday, this causes the false impression that bribes relate to Mondays, but it is only caused by the large amount of reported bribes on this specific day.

We leave out one observation in the dataset of a 2500000000 INR bribe which seems to be a misreporting. In general, the bribes categorised in *Others* seem to be less reliable and should be treated with caution.

In the following, we will simply denote the reported bribes as *bribes*.

The data clearly shows that in the observed period some provinces experience more corruption than others. Karnataka is without comparison the city with most the bribes reported. This cannot be explained by the size of its population as Karnataka is only the ninth largest state in terms of population. For instance, Uttar Pradesh and Maharashtra have more than three times the population of Karnataka[^states-india].

[^states-india]: https://en.wikipedia.org/wiki/States_and_union_territories_of_India

*Figure 1: Number of bribes paid in each province*

```{r, echo=FALSE}
ggplot(data = df, aes(x = province)) + geom_histogram() + coord_flip() + theme_minimal() + labs(x = "Province", y = "Number of bribes")
```

For Karnataka, we see that most of the bribes paid concern official documents like "Duplicating Registration Certificate" and "Issue of Ration Card". These bribes associated with official papers are a general issue in India and we will take a closer look at that later. The reason why it is a big problem in Karnataka and why this province is the most corrupted in terms of bribes paid is ambiguous. However, in India - and particularly Karnataka - the government is working on limiting the corruption[^corruption-india].

[^corruption-india]: https://en.wikipedia.org/wiki/Corruption_in_India

*Figure 2: Transactions in Karnataka*  

```{r, echo=FALSE}
ggplot(data = filter(df, province == "Karnataka"), aes(x = transaction)) + geom_histogram() + coord_flip() + theme_minimal() + labs(x = "Transaction type", y = "Number of bribes")
```


# Corruption in Official Papers and Vital Necessities

When it comes to the amount of bribes by department, it is clear that the "Municipal Services" and "Food, Civil Supplies and Consumer Affairs" departments are overrepresented. Almost all the reported bribes concern birth certificates and ration cards, which could indicate a tendency to a higher degree of corruption in official papers and vital necessities.

*Figure 3: Number of bribes in each department*

```{r, echo=FALSE}
ggplot(data = df, aes(x = department)) + geom_histogram() + coord_flip() + theme_minimal() + labs(x = "Department", y = "Number of bribes")
```

*Figure 4: Number of bribes in different transactions*

```{r, echo=FALSE}
ggplot(data = df, aes(x = transaction)) + geom_histogram() + coord_flip() + theme_minimal() + labs(x = "Transaction type", y = "Number of bribes")
```

## Ration cards

In public, a high degree of corruption within ration cards in India is well known. This applies both to the families who apply for the card, but shops, which cooperates with India's public distribution system also exploit the possibility to get fake ration cards by bribing officials. In this way the shops get a bigger ratio and they sell the extra goods at the black market. This could lead to a reasonable profit, and you could thereby assume that the bribes would be reasonable big, but from the figure below it is clear that the mean of the bribes (INR 2.220) in this area are small compared to other areas. But at the same time a few bribes are considerably larger, which could reflect that the small bribes represent poor families applying for a ration card and the big bribes represent shop owners or people who exploit the ration cards on a bigger scale.[^ration-card]

[^ration-card]: https://en.wikipedia.org/wiki/Ration_card_(India)
  
*Figure 5: Mean of bribes amount by transaction*

```{r, echo=FALSE}
df.bribes.by.transaction = df %>%
   group_by(transaction) %>%
   summarise(
      mean = mean(amount)
   )

ggplot(data = df.bribes.by.transaction, aes(x = transaction, y = mean)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + labs(x = "Transaction type", y = "Mean bribe amount") + scale_y_continuous(labels = comma)
```


## Birth Certificates

The largest area of reported bribes is issuing of birth certificates. As seen in the figure below the province Karnataka is overrepresented despite the number of inhabitants, which is in good compliance with the general level of corruption by province in India where the state as already mentioned tries to limit the corruption because it is a known problem. Also the city Bangalore which is the capital of Karnataka is rated as the most corrupt city in India.


*Figure 6: Number of Birth Certificate bribes in each province*

```{r, echo=FALSE}
ggplot(data = filter(df, transaction == "Birth Certificate"), aes(x = province)) + geom_histogram() + coord_flip() + theme_minimal() + labs(x = "Province", y = "Number of bribes")
```


The figure below shows the mean amount of the bribes by province to look for a relationship between those. It could be reasonable to expect larger bribes in the most corrupt cities. This assumption relies on the thought that when corruption has become more general it could mean the amounts raise. But it actually turns out that the provinces which are reported the most corrupt[^most-corrupt] have lower average bribes.

[^most-corrupt]: http://topyaps.com/10-corrupt-cities-india

*Figure 7: Mean amount of bribes by province*

```{r, echo=FALSE}
df.bribes.by.province = df %>%
   group_by(province) %>%
   summarise(
      mean = mean(amount)
   )

ggplot(data = df.bribes.by.province, aes(x = province, y = mean)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal()
```


# Conclusions


# Appendix

## R-code for creating dataset

```{r eval=FALSE}
# Load libraries
library(rvest)
library(stringr)
library(lubridate)
library(ggplot2)
library(dplyr)

# Scraping setup ----

# Init data frame
dt = data.frame()

# Define scraping function
scrape.bribes = function(dt, url) {
   # Select paid bribe nodes
   bribes = read_html(url) %>% html_nodes("section.ref-module-paid-bribe")

   # Extract information
   id = bribes %>% html_nodes(".unique-reference") %>% html_text() %>% str_extract("\\d+") %>% as.numeric()

   title = bribes %>% html_nodes(".heading-3") %>% html_text() %>% str_trim()

   amount = bribes %>% html_nodes(".paid-amount") %>% html_text() %>% str_extract("\\d+(,\\d+)*")
   amount = as.numeric(gsub(",", "", amount))

   department = bribes %>% html_nodes(".department > .name") %>% html_text() %>% str_trim()

   transaction = bribes %>% html_nodes(".department > .transaction") %>% html_text() %>% str_trim()

   views = bribes %>% html_nodes(".views") %>% html_text() %>% str_extract("\\d+") %>% as.numeric()

   location = bribes %>% html_nodes(".location") %>% html_text() %>% str_extract_all("\\w+", simplify = TRUE)
   city = location[,1]
   province = ifelse(ncol(location) > 2,
                     apply(location[, 2:ncol(location)], 1, function(x) str_trim(paste(x, collapse = ' '))),
                     str_trim(location[, 2]));

   Sys.setlocale("LC_TIME", "C") # fix to prevent NA from date
   date = bribes %>% html_nodes(".key > .date") %>% html_text() %>% as.Date("%B %d, %Y")

   # Append to data frame
   rbind(dt, data.frame(id, title, amount, department, transaction, views, city, province, date))
}

#
# Scrape ----
#

start = 0
max = 1000
per.page = 10
base_url = "http://ipaidabribe.com/reports/paid?page="

for (i in seq(start, max - per.page, by = per.page)) {
   url = paste(base_url, i, sep = "")

   dt = scrape.bribes(dt, url)

   print(sprintf("Scraped %d/%d bribes.", i + per.page, max))
   #Sys.sleep(1)
}

#
# Remove duplicates ----
#

dt = filter(dt, !duplicated(dt))

#
# Save data to disk ----
#

write.csv(dt, file = "D:/NewDrive/Backup/Polit/Social Data Science/bribes_061115.csv", row.names = FALSE)
```

